Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-02-28 Ben_Manuscripts/structure_paper/Draft.tex
got correct version back

  We generated an ensemble of characteristic, low-energy vacuum monomer
  configurations by applying a simulated annealing process to a
  parameterized monomer. We cooled monomers from 1000K to 50K over 10
  nanoseconds. We randomly pulled a low energy configuration from the
  trajectory then reassigned charges using \texttt{molcharge}. Using the new
  charges, we annealed the monomer system again and pulled a random monomer
  configuration from the trajectory which we used for full system
  construction (Figure~\ref{fig:python}a). See supplemental information for
  further detail.

@@

  The timescale for self-assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic simulation,
  calling for a more efficient way to build the system. Previous work has shown
  a coarse-grained model self assemble into the H\textsubscript{II} phase
  configuration in $\sim$1000 ns \cite{mondal_self-assembly_2013}.  We
  attempted atomistic self-assembly by packing monomers into a box using Packmol
  \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
  indicators of progress towards an ordered system. To bypass the slow
  self-assembly process, we use Python scripts to assemble monomers into a
  structure close to one of a number of hypothesized equilibrium configurations
  (Figure~\ref{fig:python}).
  %MRS6: question; we would like to make these releasable in GitHub.
  \begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
	\caption{(a) We parameterized a single monomer and annealed it to produce a low energy
		configuration. (b) A Python script rotates and assembles monomers into layers with 
		hydrophilic centers. (c) We chose to stack twenty layers on top of each other to create
		pores. (d) The pores are duplicated and placed into a monoclinic unit cell.}\label{fig:python}
  \end{figure}

@@

  When constructing an initial configuration, there are a number of variables
  which require careful consideration while placing monomers. The equilibrium
  configuration is sensitive to some while insensitive to others. The starting
  pore radius, defined as the distance of a chosen head group carbon from the
  pore's central axis, does not influence the equilibrium structure if one choses
  a reasonable value. The pore radius is chosen to be 0.5 nm in our initial
  configurations. 
  %MRS6: added.
  The initial distance between pores, within a wide range, also has little effect on
  the the equilibrated structure. However, one should not start them too close or
  there will be high energy repulsions during early equilibration. We chose an
  initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental value
  of 4.12 nm.  A sensitivity analysis of both parameters is presented in
  the 
  %MRS6: check for J phys chem B to see if its supporting or supplemental information or material.
  supplemental information.  The distance between layers, the rotation of the
  layers with respect to adjacent layers, and the number of monomers per layer do
  influence the equilibrium structure and require further justification for their
  choices. We rely on experimental data to inform them.

  We chose the layer spacing for the initial configuration based on R-$\pi$ and
  then allowed the system to readjust during equilibration. Each monomer was
  rotated so the plane of its aromatic head groups would be coplanar with the xy
  plane. We explored three different initial layer spacings. The first is exactly
  equal to R-$\pi$ with layers placed so aromatic rings stack 3.7 \AA~apart in
  the z-direction. We explore a second system with an initial layer spacing of 5
  \AA. We briefly explored a third system with an initial layer spacing of 10
  \AA, however it shows non-physical behavior which is detailed in the 
  Supplemental Information.

@@

  We chose the relative interlayer orientation based on clues from diffraction
  data as well as the various known stacking modes of benzene and substituted
  benzene rings: sandwiched, parallel-displaced and T-shaped
  \cite{sinnokrot_estimates_2002}. We ruled out the T-shaped configuration
  because its $\sim$5 \AA~equilibrium stacking distance
  \cite{sinnokrot_estimates_2002} is inconsistent with R-$\pi$. It is also
  infeasible for the monomers to orient in the T-shaped conformation because of
  the bulky tail groups. We will explore the system's preference towards the
  sandwiched vs. parallel displaced stacking modes in some detail. Both have
  reported stacking distances near the R-$\pi$ value of 3.7 \AA. Headgroups in
  our sandwiched initial configuration stack directly on top of each other while
  headgroups in the parallel displaced initial configuration stack with an offset
  of $180^\circ/nmon$ where $nmon$ is the number of monomers per layer. See
  the Supplemental Information for a detailed illustration of the initial
  configurations in each mode.

@@

  %MRS6: some parameters missing here (time run between insertions, etc). 
  %I assume they are in supporting information?
  In order to create a ``wet'' system, we solvated an initial configuration with
  water using \texttt{gmx solvate}. We remove all water molecules placed outside
  the pore region. Then we randomly remove water molecules inside the pore region
  until the pores reach the desired concentration of water. The remainder of the
  equilibration follows the same procedure as the dry system.

@@

  To calculate the equilibrated pore spacing, we measured the distance between
  pore centers. We located the pore centers by averaging the coordinates of sodium
  ions in their respective pores. We generated pore spacing statistics 
  using the bootstrapping technique (See Supplemental Information).

@@

  We calculated the nematic order parameter for our system in order to
  understand the degree of ordering among monomer head groups. Typically, the
  nematic order parameter is calculated for nematic liquid crystal systems which
  are characterized by unidirectional ordering of liquid crystal monomers. The
  preferred direction of monomers is defined by the unit director vector,
  $\mathbf{n}$. Assuming a single preferred direction of alignment, the nematic
  order parameter, $S$, is defined as:
  \begin{equation}
	 S = \frac{1}{2} \langle(3\cos^2\theta -1)\rangle
	\label{eqn:nematic_order_parameter}
  \end{equation}
  where $\theta$ is the angle between the molecular long axis and $\mathbf{n}$.
  In a perfectly ordered system, the molecular axis should be aligned with
  $\mathbf{n}$ and give an order parameter of $S=1$. We are interested in
  quantifying the degree of monomer head group alignment between systems. We use
  Eq.~\ref{eqn:nematic_order_parameter} to accomplish this by defining
  $\mathbf{n}$ as the z-axis (or pore axis), and then measuring the angles,
  $\theta$, between $\mathbf{n}$ and the vectors perpendicular to the plane of
  the aromatic head groups. See the supplemental information for a diagram.

@@

  \subsubsection{\textit{Radial distribution functions}}
  Closely related to the spatial correlation functions, we explored the pores'
  compositions by measuring the average number densities of various monomer
  components as a function of distance from the pore centers. We looked at the
  average number density of sodium ions, aromatic rings and carbon atoms making
  up the monomer tails. We binned the radial distance of all atoms in each group
  from the pore centers, then normalized by the volume of the annulus defined by
  the bin edges and the z box vector (See supplemental information for a 
  diagram).

@@

  Our simulations best support a model built with 5 monomers per layer based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing question (\ref{point:monomernum}), we ran
  simulations of systems created with 4--8 monomers per layer. We built systems
  in both the parallel displaced and sandwiched configurations with layers
  initially spaced 3.7 \AA~apart. We prepared equilibrated configurations
  according to the dry equilibration procedure. All systems are stable after 400
  ns of simulation. 
  %MRS6: Above, probably need to be a bit more clear what you mean by stable (no noticable drift in pore-to-pore), and if you are only using data after the point of stability.
In a sense, all systems are at least metastable, addressing
  question (\ref{point:metastable}), however not all will make physical sense or fit
  the experimental profile that we are trying to match. Figure~\ref{fig:p2p}
  shows 
%MRS6:
%the pore spacing 
the equilibrated pore-to-pore distances 
for all systems tested. 
Systems built with 5 monomers in
  each layer equilibrate to a pore spacing that is most consistent with the
  experimental value of 4.12 nm derived from SAXS measurements
  (Figure~\ref{fig:SAXS}). 
%MRS6: discuss very briefly how far off 4 and 6 are to motivate selecting 5 exclusively.
The remainder of this discussion will focus on the
  analysis of systems built with 5 monomers per layer.

@@

  The parallel displaced configuration results in a simulated XRD pattern with
  the closest match to experiment. It produces the only pattern that exhibits all
  major reflections. R-alkanes and R-pores appear as they do in the sandwiched
  configuration. R-spots and R-$\pi$ appear, however with a lower intensity
  relative to R-alkanes when compared to the sandwiched configuration. R-helix
  appears due to the parallel displaced aromatic rings. It is a subharmonic of
  R-$\pi$ since the nearest vertically stacked head group to any given head group
  is $2\times$R-$\pi$~away. 
  %BJC: adjust figure size and alignment -- probably easiest to set figure size in matplotlib
  \begin{figure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \vspace{-0.2em}
        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{offset_rzplot.png}
        \caption{}~\label{fig:rz_offset}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
%        \vspace{0.25em}
        \includegraphics[scale=0.285]{WAXS_raw.png}
        \caption{}~\label{fig:raw_waxs}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{layered_rzplot.png}
        \caption{}~\label{fig:rz_layered}
  \end{subfigure}
  \begin{subfigure}{0.0544\linewidth}
        \centering
        \vspace{-4.00em}
        \includegraphics[width=\linewidth]{colorbar_seismic.png}
  \end{subfigure}
%MRS6: question: the SAXS region looks different between sandwiched and parallel displaced. Any thoughts why? We can discuss in person.  And seems like have to comment on the difference in intensity between Sandwich and parallel displaced in the pi-pi region.
%MRS6: I wonder to what extent showing the reflections of tails removed would make it clearer pi-pi is really there.  Maybe in supporting info?
  \caption{The simulated XRD pattern generated from the equilibrated trajectory
	  of the parallel displaced configuration (a) exhibits all major reflections
	  present in the experimental WAXS pattern (b). The simulated XRD pattern
	  generated from the equilibrated trajectory in the sandwiched configuration (c) shows
	  all major reflections except R-helix.}
  \label{fig:XRDsim}
  \end{figure}

@@

  In addition to R-$\pi$ being shifted to lower $\mathbf{q}$ values, a few
  factors combine to make the simulated R-$\pi$ reflection visibly more intense
  than in the experimental pattern. The simplest reason is that R-$\pi$ and
  R-alkanes add together to boost the overall signal at interesecting values of
  $\mathbf{q}$. In addition, we observe a much higher maximum intensity within
  R-$\pi$. The maximum intensity within R-$\pi$ of the normalized experimental
  pattern is 3.1, while the maximum intensity within R-$\pi$ of the normalized
  parallel displaced simulated pattern is 32.9. 
  %MRS2 10x is really big.  That seems hard to actually manage . . . I didn't realize it was that big. For some reason, I thought it was around 3x.  If it's that big, how come the 7.4 A reflection isn't big?  It's not clear to me how this is possible. Not clear how the angle averaging obscured this before?
  While direct numerical
  comparisons between simulation and experiment aren't necessarily precise due to
  underlying assumptions, an order of magnitude difference suggests some
  significance. We believe that we see such a high maximum for two reasons: (1)
  We are simulating a perfectly aligned system so all X-rays reflected along the
  pore axis would add constructively. The crystalline domains in the real system
  are not perfectly aligned (See azimuthal distribution in supplemental
  information) which would lead to an overall decrease in the intensity of
  R-$\pi$. (2) Our system is more ordered with high correlation between layers.
  We will come back to this point further in ensuing discussions.

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
  \caption{We measured the angle made between each monomer alkane tail and the
	  membrane plane. The average tilt angle is near 7\degree~which is far from the
	  37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
  %MRS6: might want to add some discussion about how the angles are also very spread out, so there should be little signal due to tilt anywhere.
  \end{figure}

@@

%MRS6: should probably be present tense.  Maybe phrase ``in our simulations, layers are'' 
  We learned that layers are well-defined and persistent, answering question
  (\ref{point:layers}). We established our conclusion by plotting the two
  dimensional pair distribution function, $g(y,z)$ of head group phenyl rings
  using Equation~\ref{eqn:correlation} (Figure \ref{fig:yz_correlation}). In both
  configurations, the phenyl rings stack in the z-direction, along $y=0$, and
  clear layers are formed. The layers in the sandwiched configuration are more
  defined than those in the parallel displaced configuration and are strongly
  correlated with adjacent layers. We also observe correlation of layers between
  pores indicated by the non uniformity in $g(y,z)$ in adjacent columns (along $y
  = \pm 3.65$). Parallel displaced layers display weaker correlations but do not
  decay in their intensity as z increases. We do not see correlation between
%MRS6: correlations of what between pores?
  pores, however correlations within pores are strong throughout the length of
  the unit cell since there is no noticeable decay in layer intensity.

@@

  %MRS6: do you need both the 2D and 1D correlation functions?
  \begin{figure}
        \centering
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf_overlay_layered.png}
                \caption{}\label{fig:zdf_layered}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf_overlay_offset.png}
                \caption{}\label{fig:zdf_offset}
        \end{subfigure}
	\caption{We support the existence of layers with the observance of
		clear periodic maxima in the $z$-direction pair distribution functions of the
		(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, parallel
		displaced configurations. The extent to which we consider a system to be
		layered is based on the magnitude of the deviation of the periodic maxima from
		the average number density. The sandwiched configuration possesses a higher
		degree of layering than the parallel displaced configuration and, in both
		cases, the head group region has a higher degree of layer partitioning than the
		tail region. (See supplemental information for detailed definitions of the head
		group and tail regions)}\label{fig:zdf}
  \end{figure}

@@

  Correlation lengths are shorter in the disordered pore basin than in the
  ordered pore basin. Layers in the ordered pore basin are strongly correlated
  with neighboring layers up to more than 10 layers away. This behavior deviates
  from experimental evidence. The experimental correlation length (See
  supplemental information for details its derivation) suggests that layers are
  correlated with about 3 neighboring layers which is closer to the values
  exhibited by the disordered pore basin. We may need to simulate a system with
  many more layers in order to reduce the correlation contributed by periodic
  copies of the system.

%MRS6: not sure if we WANT to do this, but could do a simulation with 2x as many layers and see if the correlation changes.

  We calculated the nematic order parameter for each system using Equation
  \ref{eqn:nematic_order_parameter}. The calculated values of S are presented in
  Table \ref{table:nematic}. The full distributions of angles between director
  \textbf{n} and vectors orthogonal to monomer phenyl rings are presented in the
  supplemental material. In general, ordered pore basin systems are more
  nematically ordered than disordered pore basin systems and sandwiched
  configuration systems are more nematically ordered than parallel displaced
  configuration systems. The head groups of the disordered pore basin have more
  rotational freedom about the xy plane likely due to the larger separation
  between layers. Similarly, monomers situated in the sandwiched configuration
  are constrained by other monomers stacked directly above and below them, while
  monomers in the parallel displaced configuration have no direct neighbors
  vertically which provides them with more rotational freedom.

@@

%MRS: I think you will need to refer back to names of the questions (or at least shortened versions of the names): people skimming the paper will not remember what the numbers are.
  In order to address question (\ref{point:poredefinition}), we plotted the
  number densities of heavy atoms in the head group, carbon atoms in the tail
  region and all sodium ions (Figure~\ref{fig:densities}). For the head group
  region, we used the carbon atoms making up the aromatic ring. For the tail
  region we used only carbon atoms of the monomer tails (See Supplemental
  Information for diagram). We average the histograms over at least 50 ns of
  equilibrated trajectory.

>>>>

  We generated an ensemble of characteristic, low-energy vacuum monomer
  configurations by applying a simulated annealing process to a
  parameterized monomer. We cooled monomers from 1000K to 50K over 10
  nanoseconds. We randomly pulled a low energy configuration from the
  trajectory then reassigned charges using \texttt{molcharge}. Using the new
  charges, we annealed the monomer system again and pulled a random monomer
  configuration from the trajectory which we used for full system
  construction (Figure~\ref{fig:python}a). See Supporting Information for
  further detail.

@@

  The timescale for self-assembly of monomers into the hexagonal phase is
  unknown and likely outside of a reasonable length for an atomistic simulation,
  calling for a more efficient way to build the system. Previous work has shown
  a coarse-grained model self assemble into the H\textsubscript{II} phase
  configuration in $\sim$1000 ns \cite{mondal_self-assembly_2013}.  We
  attempted atomistic self-assembly by packing monomers into a box using Packmol
  \cite{martinez_packmol:_2009}. Simulations of greater than 100 ns show no
  indicators of progress towards an ordered system. To bypass the slow
  self-assembly process, we use Python scripts to assemble monomers into a
  structure close to one of a number of hypothesized equilibrium configurations
  (Figure~\ref{fig:python}).
  %MRS6: question; we would like to make these releasable in GitHub.
  %BJC2: yes .. what is the question?
  \begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{build.PNG} %BJC: put an xyz axis with the unit cell
	\caption{(a) We parameterized a single monomer and annealed it to produce a low energy
		configuration. (b) A Python script rotates and assembles monomers into layers with 
		hydrophilic centers. (c) We chose to stack twenty layers on top of each other to create
		pores. (d) The pores are duplicated and placed into a monoclinic unit cell.}\label{fig:python}
  \end{figure}

@@

  When constructing an initial configuration, there are a number of variables
  which require careful consideration while placing monomers. The equilibrium
  configuration is sensitive to some while insensitive to others. The starting
  pore radius, defined as the distance of a chosen head group carbon from the
  pore's central axis, does not influence the equilibrium structure if one choses
  a reasonable value. The pore radius is chosen to be 0.5 nm in our initial
  configurations. 
  %MRS6: added.
  The initial distance between pores, within a wide range, also has little effect on
  the the equilibrated structure. However, one should not start them too close or
  there will be high energy repulsions during early equilibration. We chose an
  initial pore spacing of 4.5 nm, $\sim$10\% larger than the experimental value
  of 4.12 nm.  A sensitivity analysis of both parameters is presented in
  the 
  %MRS6: check for J phys chem B to see if its supporting or supplemental information or material.
  %BJC2: good point. It is 'supporting information'
  Supporting information.  The distance between layers, the rotation of the
  layers with respect to adjacent layers, and the number of monomers per layer do
  influence the equilibrium structure and require further justification for their
  choices. We rely on experimental data to inform them.

  We chose the layer spacing for the initial configuration based on R-$\pi$ and
  then allowed the system to readjust during equilibration. Each monomer was
  rotated so the plane of its aromatic head groups would be coplanar with the xy
  plane. We explored three different initial layer spacings. The first is exactly
  equal to R-$\pi$ with layers placed so aromatic rings stack 3.7 \AA~apart in
  the z-direction. We explore a second system with an initial layer spacing of 5
  \AA. We briefly explored a third system with an initial layer spacing of 10
  \AA, however it shows non-physical behavior which is detailed in the 
  Supporting Information.

@@

  We chose the relative interlayer orientation based on clues from diffraction
  data as well as the various known stacking modes of benzene and substituted
  benzene rings: sandwiched, parallel-displaced and T-shaped
  \cite{sinnokrot_estimates_2002}. We ruled out the T-shaped configuration
  because its $\sim$5 \AA~equilibrium stacking distance
  \cite{sinnokrot_estimates_2002} is inconsistent with R-$\pi$. It is also
  infeasible for the monomers to orient in the T-shaped conformation because of
  the bulky tail groups. We will explore the system's preference towards the
  sandwiched vs. parallel displaced stacking modes in some detail. Both have
  reported stacking distances near the R-$\pi$ value of 3.7 \AA. Headgroups in
  our sandwiched initial configuration stack directly on top of each other while
  headgroups in the parallel displaced initial configuration stack with an offset
  of $180^\circ/nmon$ where $nmon$ is the number of monomers per layer. See
  the Supporting Information for a detailed illustration of the initial
  configurations in each mode.

@@

  %MRS6: some parameters missing here (time run between insertions, etc). 
  %I assume they are in supporting information?
  %BJC2: Not there yet but will add
  In order to create a ``wet'' system, we solvated an initial configuration with
  water using \texttt{gmx solvate}. We remove all water molecules placed outside
  the pore region. Then we randomly remove water molecules inside the pore region
  until the pores reach the desired concentration of water. The remainder of the
  equilibration follows the same procedure as the dry system.

@@

  To calculate the equilibrated pore spacing, we measured the distance between
  pore centers. We located the pore centers by averaging the coordinates of sodium
  ions in their respective pores. We generated pore spacing statistics 
  using the bootstrapping technique (See Supporting Information).

@@

  We calculated the nematic order parameter for our system in order to
  understand the degree of ordering among monomer head groups. Typically, the
  nematic order parameter is calculated for nematic liquid crystal systems which
  are characterized by unidirectional ordering of liquid crystal monomers. The
  preferred direction of monomers is defined by the unit director vector,
  $\mathbf{n}$. Assuming a single preferred direction of alignment, the nematic
  order parameter, $S$, is defined as:
  \begin{equation}
	 S = \frac{1}{2} \langle(3\cos^2\theta -1)\rangle
	\label{eqn:nematic_order_parameter}
  \end{equation}
  where $\theta$ is the angle between the molecular long axis and $\mathbf{n}$.
  In a perfectly ordered system, the molecular axis should be aligned with
  $\mathbf{n}$ and give an order parameter of $S=1$. We are interested in
  quantifying the degree of monomer head group alignment between systems. We use
  Eq.~\ref{eqn:nematic_order_parameter} to accomplish this by defining
  $\mathbf{n}$ as the z-axis (or pore axis), and then measuring the angles,
  $\theta$, between $\mathbf{n}$ and the vectors perpendicular to the plane of
  the aromatic head groups. See the Supporting Information for a diagram.

@@

  \subsubsection{\textit{Radial distribution functions}}
  Closely related to the spatial correlation functions, we explored the pores'
  compositions by measuring the average number densities of various monomer
  components as a function of distance from the pore centers. We looked at the
  average number density of sodium ions, aromatic rings and carbon atoms making
  up the monomer tails. We binned the radial distance of all atoms in each group
  from the pore centers, then normalized by the volume of the annulus defined by
  the bin edges and the z box vector (See Supporting Information for a 
  diagram).

@@

  Our simulations best support a model built with 5 monomers per layer based on
  the measured equilibrated pore-to-pore distances. To discern the composition of
  the monomer layers, addressing question (\ref{point:monomernum}), we ran
  simulations of systems created with 4--8 monomers per layer. We built systems
  in both the parallel displaced and sandwiched configurations with layers
  initially spaced 3.7 \AA~apart. We prepared equilibrated configurations
  according to the dry equilibration procedure. All systems are stable after 400
  ns of simulation. 
  %MRS6: Above, probably need to be a bit more clear what you mean by stable (no noticable drift in pore-to-pore), and if you are only using data after the point of stability.
  %BJC2: I believe this is included in methods. I can restate if that's not clear
In a sense, all systems are at least metastable, addressing
  question (\ref{point:metastable}), however not all will make physical sense or fit
  the experimental profile that we are trying to match. Figure~\ref{fig:p2p}
  shows 
%MRS6:
%the pore spacing 
the equilibrated pore-to-pore distances 
for all systems tested. 
Systems built with 5 monomers in
  each layer equilibrate to a pore spacing that is most consistent with the
  experimental value of 4.12 nm derived from SAXS measurements
  (Figure~\ref{fig:SAXS}). 
%MRS6: discuss very briefly how far off 4 and 6 are to motivate selecting 5 exclusively.
The remainder of this discussion will focus on the
  analysis of systems built with 5 monomers per layer.

@@

  The parallel displaced configuration results in a simulated XRD pattern with
  the closest match to experiment. It produces the only pattern that exhibits all
  major reflections. R-alkanes and R-pores appear as they do in the sandwiched
  configuration. R-spots and R-$\pi$ appear, however with a lower intensity
  relative to R-alkanes when compared to the sandwiched configuration. R-helix
  appears due to the parallel displaced aromatic rings. It is a subharmonic of
  R-$\pi$ since the nearest vertically stacked head group to any given head group
  is $2\times$R-$\pi$~away. 
  %BJC: adjust figure size and alignment -- probably easiest to set figure size in matplotlib
  \begin{figure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \vspace{-0.2em}
        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{offset_rzplot.png}
        \caption{}~\label{fig:rz_offset}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
%        \vspace{0.25em}
        \includegraphics[scale=0.285]{WAXS_raw.png}
        \caption{}~\label{fig:raw_waxs}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
        \centering
        \includegraphics[width=1.1\linewidth,trim={1cm 0 1.3cm 0},clip]{layered_rzplot.png}
        \caption{}~\label{fig:rz_layered}
  \end{subfigure}
  \begin{subfigure}{0.0544\linewidth}
        \centering
        \vspace{-4.00em}
        \includegraphics[width=\linewidth]{colorbar_seismic.png}
  \end{subfigure}
%MRS6: question: the SAXS region looks different between sandwiched and parallel displaced. Any thoughts why? We can discuss in person.  And seems like have to comment on the difference in intensity between Sandwich and parallel displaced in the pi-pi region.
%MRS6: I wonder to what extent showing the reflections of tails removed would make it clearer pi-pi is really there.  Maybe in supporting info?
%BJC2: Sure, I'll add that to supporting info
  \caption{The simulated XRD pattern generated from the equilibrated trajectory
	  of the parallel displaced configuration (a) exhibits all major reflections
	  present in the experimental WAXS pattern (b). The simulated XRD pattern
	  generated from the equilibrated trajectory in the sandwiched configuration (c) shows
	  all major reflections except R-helix.}
  \label{fig:XRDsim}
  \end{figure}

@@

  In addition to R-$\pi$ being shifted to lower $\mathbf{q}$ values, a few
  factors combine to make the simulated R-$\pi$ reflection visibly more intense
  than in the experimental pattern. The simplest reason is that R-$\pi$ and
  R-alkanes add together to boost the overall signal at interesecting values of
  $\mathbf{q}$. In addition, we observe a much higher maximum intensity within
  R-$\pi$. The maximum intensity within R-$\pi$ of the normalized experimental
  pattern is 3.1, while the maximum intensity within R-$\pi$ of the normalized
  parallel displaced simulated pattern is 32.9. 
  %MRS2 10x is really big.  That seems hard to actually manage . . . I didn't realize it was that big. For some reason, I thought it was around 3x.  If it's that big, how come the 7.4 A reflection isn't big?  It's not clear to me how this is possible. Not clear how the angle averaging obscured this before?
  %BJC2 From plots of raw structure factor, it doesn't seem like a normalization issue. It was probably obscured in the orginal angle averaging because it 
  % was averaged with neighboring bins
  While direct numerical
  comparisons between simulation and experiment aren't necessarily precise due to
  underlying assumptions, an order of magnitude difference suggests some
  significance. We believe that we see such a high maximum for two reasons: (1)
  We are simulating a perfectly aligned system so all X-rays reflected along the
  pore axis would add constructively. The crystalline domains in the real system
  are not perfectly aligned (See azimuthal distribution in Supporting
  Information) which would lead to an overall decrease in the intensity of
  R-$\pi$. (2) Our system is more ordered with high correlation between layers.
  We will come back to this point further in ensuing discussions.

@@

  \begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{tilt_dist.png}
  \caption{We measured the angle made between each monomer alkane tail and the
	  membrane plane. The average tilt angle is near 7\degree~which is far from the
	  37\degree~tilt angle previously used to explain R-spots.}~\label{fig:tilt}
  %MRS6: might want to add some discussion about how the angles are also very spread out, so there should be little signal due to tilt anywhere.
  %BJC2: good idea
  \end{figure}

@@

%MRS6: should probably be present tense.  Maybe phrase ``in our simulations, layers are'' 
  In our simulations, layers are well-defined and persistent, answering question
  (\ref{point:layers}). We established our conclusion by plotting the two
  dimensional pair distribution function, $g(y,z)$ of head group phenyl rings
  using Equation~\ref{eqn:correlation} (Figure \ref{fig:yz_correlation}). In both
  configurations, the phenyl rings stack in the z-direction, along $y=0$, and
  clear layers are formed. The layers in the sandwiched configuration are more
  defined than those in the parallel displaced configuration and are strongly
  correlated with adjacent layers. We also observe correlation of layers between
  pores indicated by the non uniformity in $g(y,z)$ in adjacent columns (along $y
  = \pm 3.65$). Parallel displaced layers display weaker correlations but do not
  decay in their intensity as z increases. We do not see correlation between
%MRS6: correlations of what between pores?
  pores, however correlations within pores are strong throughout the length of
  the unit cell since there is no noticeable decay in layer intensity.

@@

  %MRS6: do you need both the 2D and 1D correlation functions?
  \begin{figure}
        \centering
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf_overlay_layered.png}
                \caption{}\label{fig:zdf_layered}
        \end{subfigure}
        \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{zdf_overlay_offset.png}
                \caption{}\label{fig:zdf_offset}
        \end{subfigure}
	\caption{We support the existence of layers with the observance of
		clear periodic maxima in the $z$-direction pair distribution functions of the
		(a) 5 monomer per layer, sandwiched and (b) 5 monomer per layer, parallel
		displaced configurations. The extent to which we consider a system to be
		layered is based on the magnitude of the deviation of the periodic maxima from
		the average number density. The sandwiched configuration possesses a higher
		degree of layering than the parallel displaced configuration and, in both
		cases, the head group region has a higher degree of layer partitioning than the
		tail region. (See Supporting information for detailed definitions of the head
		group and tail regions)}\label{fig:zdf}
  \end{figure}

@@

  Correlation lengths are shorter in the disordered pore basin than in the
  ordered pore basin. Layers in the ordered pore basin are strongly correlated
  with neighboring layers up to more than 10 layers away. This behavior deviates
  from experimental evidence. The experimental correlation length (See
  Suppporting Information for details its derivation) suggests that layers are
  correlated with about 3 neighboring layers which is closer to the values
  exhibited by the disordered pore basin. We may need to simulate a system with
  many more layers in order to reduce the correlation contributed by periodic
  copies of the system.

%MRS6: not sure if we WANT to do this, but could do a simulation with 2x as many layers and see if the correlation changes.
%BJC2: have one that is 3x going right now

  We calculated the nematic order parameter for each system using Equation
  \ref{eqn:nematic_order_parameter}. The calculated values of S are presented in
  Table \ref{table:nematic}. The full distributions of angles between director
  \textbf{n} and vectors orthogonal to monomer phenyl rings are presented in the
  Supporting Information. In general, ordered pore basin systems are more
  nematically ordered than disordered pore basin systems and sandwiched
  configuration systems are more nematically ordered than parallel displaced
  configuration systems. The head groups of the disordered pore basin have more
  rotational freedom about the xy plane likely due to the larger separation
  between layers. Similarly, monomers situated in the sandwiched configuration
  are constrained by other monomers stacked directly above and below them, while
  monomers in the parallel displaced configuration have no direct neighbors
  vertically which provides them with more rotational freedom.

@@

%MRS: I think you will need to refer back to names of the questions (or at least shortened versions of the names): people skimming the paper will not remember what the numbers are.
  In order to address question (\ref{point:poredefinition}), we plotted the
  number densities of heavy atoms in the head group, carbon atoms in the tail
  region and all sodium ions (Figure~\ref{fig:densities}). For the head group
  region, we used the carbon atoms making up the aromatic ring. For the tail
  region we used only carbon atoms of the monomer tails (See Supporting
  Information for diagram). We average the histograms over at least 50 ns of
  equilibrated trajectory.
